Recurrent Neural Networks for video object detection

### 2019-07-30 Paper/Paper_First_Draft.tex

\begin{abstract}
ToDo
\end{abstract}

\begin{IEEEkeywords}
TBD.
\end{IEEEkeywords}

@@

\subsection{Recurrent Neural Networks in general}
\subsubsection{Delimitation to non-recurrent Neural Networks} 
Non-recurrent Neural Networks process on single inputs for example, a single image. Recurrent Neural Networks process on sequences of data, e.g.: multiple video frames. Recurrent Neural Network's core concept to enable the sequence processing is parameter sharing across different parts of a model. Parameter sharing can be reached by cycles in the architecture. \cite{11} \newline

\subsubsection{Common Types of Recurent Neural Networks}
Most of the papers which are described in this work use two common Recurrent Neural Network approaches. The first one are LSTMs, first mentioned in \cite{18} in 1997. The key of LSTMs are different gates (forget gate, external input gate, output gate) to control the cell state and the hidden state of the LSTM \cite{11}.  \newline

The second type of Recurrent Neural Networks are Gated Recurrent Units (GRUs). The main difference to LSTMs is, that those GRUs consist out of a single gated unit which can simultaneously control the forgetting factor and decide to update the inner cell state. \cite{11}

@@

\subsection{Recurrent Multi-frame Single Shot Detector for Video Object Detection [1]}
Broad, Jones and Lee have in \cite{1} and \cite{12} the idea to design a multi-frame video object detector by inserting a fusion-layer into a classical Single Shot Detector (SSD) meta-architecture. Based on this idea they research in two main fields: On the one hand, they investigate different fusion methods and on the other hand they try several SSD meta-architectures [20-2.1.1; 20-3.6.1]. They test their approaches on the KITTI dataset \cite{21} for autonomous driving and their model improves upon a state-of-the-art SSD model by 2.7 \% mAP. Finally they evaluate their best approach on Caltech Pedestrians Dataset \cite{22} and find similar improvements of 5 \% in maP.   \newline

@@

In addition Broad, Jones and Lee test different types of SSDs as a baseline for their architecture. For all baseline SSDs the mAP was higher in comparison to the non-recurrent models. The mAP increase by 1.4 to 4.4 percent on KITTI dataset.  The best mAP is made with SqueezeDet+ \cite{23} as a baseline SSD network [1-4.2].  \newline

@@

\subsection{Mobile Video Object Detection with Temporally Aware Feature Maps [2]}
Liu and Zhu have in \cite{2} the goal to design a video object detection architecture, which can run real-time (15 fps) on low-powered mobile and embedded devices. The key of their method is to combine convolutional layers with convolutional LSTMs. They investigate on the benefit from adding an LSTM into the baseline SSD, different types of Recurrent Layers (LSTM, GRU and bottleneck LSTMs), different dimensions of their bottleneck LSTMs and different LSTM placement strategies (Single LSTM placement and multiple LSTM placement). They test their model on Imagenet VID 2015 dataset and reached a mAP of 54.4 \% while performing on 15 fps.  \newline

In the beginning they simply add one LSTM to their baseline SSDs architecture - MobileNet \cite{24}. They observe that adding the LSTM improves the mAP in comparison to their baseline SSD architecture. Moreover, they investigate that the greatest improve is by adding the LSTM after the 13th convolutional Layer of the SSD. [2-4.2] \newline

@@

\begin{figure} [h]
\includegraphics[width=\columnwidth]{Liu_Zhu}
\caption{Architecture Mobile Video Object Detection with temporally aware feature maps \cite{2}. First 13 Convolutional Layeer create Feature Maps. Those Feature Maps are fed into the Bottleneck-LSTMs (faster LSTMs). Afterwards Convolutional-Layer create new Feature Maps and feed them again into Bottleneck-LSTMs.}
\end{figure}

@@

Liu and Zhu confirm the observation from \cite{1} that adding temporal context information with the help recurrent units improves the detection quality of the baseline SSDs. Moreover they show that architectures using recurrent units can still perform in real-time (15 fps) even on mobile devices. In comparison to the Mobilnet-SSD model they improve the mAP by 4.1 percentage and perform faster on Pixel 2 Phone. Overall they reach an 54.4 \% on Imagenet VID. \newline

@@

The final architecture can be found in \textbf{Fig 2}. Tripathi, Lipton and Belongie first train a pretrained YOLO object detection network \cite{b20} as a  pseudo-labeler on the YouTube-Video Dataset. As specified in YOLO  they minimize the weighted squared detection loss and optimize classification and localization error simultaneously [4-3].

@@

\subsection{Deep Feature Flow for Video Recognition \cite{2}}
Zhu, Xiong, Dai, Yuan and Wei develop in \cite{b2} a way to use flow nets to detect objects in video frames. As shown in figure 10 their architecture consists of three main parts: A network to create visual features, a network to create class probabilities and bounding boxes respectively the segmentation out of feature maps, and a network which estimates the optical flow. They tested their approach on the Cityscapes dataset with scenes for autonomous driving and ground-truth for semantic segmentation and the ImageNet VID dataset with ground truth for object detection.

>>>>

\begin{abstract}
There is lot of scientific work about object detection in images. For many applications like for example autonomous driving the actual data on which classification has to be done are videos. This work compares different methods especially those which use Recurrent Neural Networks to detect objects in videos. We differ between feature-based methods, which feed feature maps of different frames into the recurrent units, box-level methods, which feed bounding boxes with class probabilities into the recurrent units and methods which use flow networks. This study indicates common outcomes of the compared methods like the benefit of including the temporal context into object detection and states conclusions and guidelines for video object detection networks. 
\end{abstract}

\begin{IEEEkeywords}
RNN; Recurrent Neural Networks; Video Object Detection; Flow Networks; Neural Networks
\end{IEEEkeywords}

@@

\subsection{Recurrent Neural Networks in general}
\subsubsection{Delimitation to non-recurrent Neural Networks} 
Non-recurrent Neural Networks process on single inputs for example, a single image. Recurrent Neural Networks process on sequences of data, e.g.: multiple video frames. Recurrent Neural Network's core concept to enable the sequence processing is parameter sharing across different parts of a model. Parameter sharing can be reached by cycles in the architecture. \cite{b11} \newline

\subsubsection{Common Types of Recurent Neural Networks}
Most of the papers which are described in this work use two common Recurrent Neural Network approaches. The first one are LSTMs, first mentioned in \cite{b18} in 1997. The key of LSTMs are different gates (forget gate, external input gate, output gate) to control the cell state and the hidden state of the LSTM \cite{b11}.  \newline

The second type of Recurrent Neural Networks are Gated Recurrent Units (GRUs). The main difference to LSTMs is, that those GRUs consist out of a single gated unit which can simultaneously control the forgetting factor and decide to update the inner cell state. \cite{b11}

@@

\subsection{Recurrent Multi-frame Single Shot Detector for Video Object Detection [1]}
Broad, Jones and Lee have in \cite{b1} and \cite{b12} the idea to design a multi-frame video object detector by inserting a fusion-layer into a classical Single Shot Detector (SSD) meta-architecture. Based on this idea they research in two main fields: On the one hand, they investigate different fusion methods and on the other hand they try several SSD meta-architectures [20-2.1.1; 20-3.6.1]. They test their approaches on the KITTI dataset \cite{b21} for autonomous driving and their model improves upon a state-of-the-art SSD model by 2.7 \% mAP. Finally they evaluate their best approach on Caltech Pedestrians Dataset \cite{b22} and find similar improvements of 5 \% in maP.   \newline

@@

In addition Broad, Jones and Lee test different types of SSDs as a baseline for their architecture. For all baseline SSDs the mAP was higher in comparison to the non-recurrent models. The mAP increase by 1.4 to 4.4 percent on KITTI dataset.  The best mAP is made with SqueezeDet+ \cite{b23} as a baseline SSD network [1-4.2].  \newline

@@

\subsection{Mobile Video Object Detection with Temporally Aware Feature Maps [2]}
Liu and Zhu have in \cite{b2} the goal to design a video object detection architecture, which can run real-time (15 fps) on low-powered mobile and embedded devices. The key of their method is to combine convolutional layers with convolutional LSTMs. They investigate on the benefit from adding an LSTM into the baseline SSD, different types of Recurrent Layers (LSTM, GRU and bottleneck LSTMs), different dimensions of their bottleneck LSTMs and different LSTM placement strategies (Single LSTM placement and multiple LSTM placement). They test their model on Imagenet VID 2015 dataset \cite{b35} and reached a mAP of 54.4 \% while performing on 15 fps.  \newline

In the beginning they simply add one LSTM to their baseline SSDs architecture - MobileNet \cite{b24}. They observe that adding the LSTM improves the mAP in comparison to their baseline SSD architecture. Moreover, they investigate that the greatest improve is by adding the LSTM after the 13th convolutional Layer of the SSD. [2-4.2] \newline

@@

\begin{figure} [h]
\includegraphics[width=\columnwidth]{Liu_Zhu}
\caption{Architecture Mobile Video Object Detection with temporally aware feature maps \cite{b2}. First 13 Convolutional Layeer create Feature Maps. Those Feature Maps are fed into the Bottleneck-LSTMs (faster LSTMs). Afterwards Convolutional-Layer create new Feature Maps and feed them again into Bottleneck-LSTMs.}
\end{figure}

@@

Liu and Zhu confirm the observation from \cite{b1} that adding temporal context information with the help recurrent units improves the detection quality of the baseline SSDs. Moreover they show that architectures using recurrent units can still perform in real-time (15 fps) even on mobile devices. In comparison to the Mobilnet-SSD model they improve the mAP by 4.1 percentage and perform faster on Pixel 2 Phone. Overall they reach an 54.4 \% on Imagenet VID. \newline

@@

The final architecture can be found in \textbf{Fig 10}. Tripathi, Lipton and Belongie first train a pretrained YOLO object detection network \cite{b20} as a  pseudo-labeler on the YouTube-Video Dataset. As specified in YOLO  they minimize the weighted squared detection loss and optimize classification and localization error simultaneously [4-3].

@@

\subsection{Deep Feature Flow for Video Recognition \cite{2}}
Zhu, Xiong, Dai, Yuan and Wei develop in \cite{b2} a way to use flow nets to detect objects in video frames. As shown in figure 10 their architecture consists of three main parts: A network to create visual features, a network to create class probabilities and bounding boxes respectively the segmentation out of feature maps, and a network which estimates the optical flow. They tested their approach on the Cityscapes dataset with scenes for autonomous driving and ground-truth for semantic segmentation and the ImageNet VID dataset \cite{b35} with ground truth for object detection.
